### 2015-04-12 draft.tex
..

\documentclass[12pt]{article}
\usepackage{times}
\usepackage{latexsym}
\usepackage[bottom=20mm, top=20mm, left=20mm, right=20mm]{geometry}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{bussproofs}
\usepackage{comment}
\usepackage[numbers]{natbib}
\usepackage{graphicx} % Graphics support
\usepackage{caption} % Improved captions
\usepackage{subfig} % Inclusion of subfigures
%\usepackage{subfigure}

@@

\begin{document}
\quad \\
\quad \\
\quad \\
\centerline{ \large{Towards Range-Based Network Synthesis}}
\vspace{1pt}\\
\centerline{Ryan Beckett and Olivier Savary B\'{e}langer} \\
\\
\centerline{April 15, 2015} \\

\section*{Introduction}
% Including an example policy

@@

@@

>>>>

\documentclass[12pt]{article}
\usepackage{times}
\usepackage{latexsym}
\usepackage[bottom=20mm, top=20mm, left=20mm, right=20mm]{geometry}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{bussproofs}
\usepackage{comment}
\usepackage[numbers]{natbib}
\usepackage{graphicx} % Graphics support
\usepackage{caption} % Improved captions
\usepackage{subfig} % Inclusion of subfigures
%\usepackage{subfigure}

@@

\begin{document}
\quad \\
\quad \\
\quad \\
\centerline{ \large{Red Oak: Something Something Algorithmic Policy}}
\vspace{1pt}\\
\centerline{Ryan Beckett and Olivier Savary B\'{e}langer} \\
\\
\centerline{April 15, 2015} \\

\section*{Introduction}
% possibly in introduction instead?
Maple \cite{Maple} proposes a SDN controller model where the behavior of the controller is defined by a function from packets to forwarding path, the algorithmic policy. The authors then show how to optimize the controller so that packets are handled without having to run the function on them. Maple does so by providing a packet API capturing each access to packet fields, and memoizing the results of the function for subsequent packets sharing the accessed fields' values. We identify a number of shortcoming to this model:
\begin{enumerate}
\item % packet value granularity too fine
  \item % environmentgranularity too fine, no built-in support for dynamic controllers
  \item % not proactive
\end{enumerate}

We present a new iteration of the model where
\begin{enumerate}
  \item calls to our API does not expose the values of a packet's field, answering instead boolean queries about the values being in a certain range
  \item dynamic controllers are supported through a relation data-structure which is updated through an extended API
  \item the trace tree can be generated from executing the policy on a single (potentially symbolic) packet.
\end{enumerate}

% Including an example policy

\begin{figure}
\begin{lstlisting}
f(pkt):
  if RO.InRange(pkt, src, 0, 10) then
     RO.add(pkt, (dst, src), conn);
     fw(gateway)
  else if (RO.InSet(pkt, (src,dst), conn) then
         fw(dst)   
       else
         drop
       end
  end                
  \end{lstlisting}

\caption{A Stateful Firewall}
\end{figure}

@@

   \begin{figure}
\begin{lstlisting}
Module RO

Type pkt (* contains a range for each field *)

Type field (* enum each field *)

function InRange: pkt * field * value * value -> bool

\end{lstlisting}

\caption{Signature of the packet portion of the API}
\end{figure}

   % Can represent constraints on the ranges admissible given a certain topology as a series of ``true'' branches at the root of the tree.

@@

   \begin{figure}
     \begin{lstlisting}

function InRange: pkt * field * value * value -> bool

\end{lstlisting}

\caption{Signature of the relation portion of the API}
\end{figure}
